Malacology: A Programmable Storage System

### 2016-10-20 paper/paper.tex
comment

\noindent\textbf{The Malacology Approach:} Re-use the capability management
features of the MDS.  While the batching mechanism can achieve high-throughput,
it is not appropriate for applications that require predictable latency. The
throughput in Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a
centralized sequencer implementation. While throughput is lower for two clients
(because of the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.\\

\noindent\textbf{Features:} delay and quota parameters control throughput vs.
latency

>>>>

\noindent\textbf{The Malacology Approach:} Re-use the capability management
features of the MDS.  While the batching mechanism can achieve high throughput,
it is not appropriate for applications that require predictable latency. The
throughput in Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a
centralized sequencer implementation. While throughput is lower for two clients
(because of the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.\\

\noindent\textbf{Features:} delay and quota parameters control throughput vs.
latency
\paa{this should probably be a complete sentence or sentences.  also, I don't recall
seeing any discussion of quotas}
